---
title: "R Open Lab 6"
author: "Hannah Ji"
date: "2018/10/29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

character : a symbol in a written language - anything you can enter on a keyboard.
string : a sequence of characters ("Columbia University")

Both are type 'character' in R.


Some special characters
```{r}
# Whitespace
class(" ")
nchar("")
nchar(" ")
nchar("  ")

# Other special character
nchar("\n")#new line
nchar("\t")#tab
nchar("\"")#quote itself
```


When strings are elements of an object(vector)
```{r}
#length return how many strings in the vector, not the number of characters in each string
length(c("we", "love", "R"))
length("we, love, R")
nchar("we, love, R")


nchar(c("we", "love", "R"))
```

cat() can coerces its argument to string
```{r}
x <- 6
y <- 7
cat("I have", x, "cats and", y, "dogs.")
#print("I have", x, "cats and", y, "dogs.")


# cat() can handle "\n", "\t" and "\""
# Check
# We want Columbia tab University
# We want quote in sentence
cat("This is an 'array'")
cat('This is an "array"')

# cannot work
#cat("This is an "array"")
#cat('This is an 'array'')
# Remedy
cat("This is an \"array\"")
cat('This is an \'array\'')
# How many character in it?
```

Substring
```{r}
mystr <- "This is R Programming Open Lab"
substr(mystr, start = 9, stop = 21)

# Need to avoid
substr(mystr, start = 9, stop = 100)# arbitary large end number

substr(mystr, start = 9, stop = 21) <- "Python"# it will just substitute according to the certain amount of new string
mystr
mystr <- "This is R programming Open Lab"
substr(mystr, start = 9, stop = 9) <- 'Python'
mystr

mystr <- "This is R Programming Open Lab"
substr(mystr, start = 9, stop = 9) <- "a"
mystr



# start and end apply to each element in the vector
fav_animals <- c("cat", "elephant", "squirrel")
substr(fav_animals, start = 1, stop = 2)
substr(fav_animals, nchar(fav_animals)-1, nchar(fav_animals))
# what will happen then?
substr(fav_animals, start = 4, stop = 4)
```

Divide strings into vectors
```{r}
# we need to have some pattern to split the string
fruit <- "Apple Banana Orange"
strsplit(fruit, split = " ")

courses <- "Lecture, Lab, Homework"
strsplit(courses, split = ",")
# strsplit(course, split = ", ")

# if input has mistake, we need to find the pattern that for our proble,
skills <-"Data,Science, Machine Learning, Programming"
strsplit(skills, split = ", ")
```


Task
```{r}
# use substr to extract "bi" in each element of a vector

substr(c("Columbia", "combine"), start = c(6,4), stop = c(7,5))

strsplit(c("Columbia", "combine"), split = "bi")
```

Build strings from multiple part
```{r}
fav_animals
paste(fav_animals, " (", 1:3, ")", sep = "  ", collapse = "; ")
```


Searching strings
```{r}
# use Tab to find file
HC <- readLines("HonorCode.txt")
# How many lines in total
length(HC)

#grep: search for a specified substring given by pattern in a vector
grep("honest", HC)
grep("students", HC)
HC[grep("honest",HC)]


#
HC_new <- paste(HC, collapse = " ") #long string
unlist(strsplit(HC_new, split = " "))
strsplit(HC_new, split = " ")[[1]]
HC.words <- strsplit(HC_new, split = " ")[[1]]
word_count <- table(HC.words)
word_count <- sort(word_count, decreasing = TRUE)

#wordcloud::wordcloud(names(word_count), word_count)
#new <- word_count[10:30]
#wordcloud::wordcloud(names(new), new)
```

```{r}
semicolons <- grep(";", HC)
HC[semicolons]
# gsub: replace patterns in a strign with another string
HC <- gsub(";", "", HC)
HC[semicolons]

mystr <- "This is R Programming Open Lab"
gsub("R Programming","Python", mystr)
```



